Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-12 src/tex/ms.tex
justify bb approximation
start stronger

\section{Introduction}
\label{sec:intro}
\rev{While the probability of abiogenesis is unknown and has primarily been explored through statistical arguments~\citep[e.g.,][]{Spiegel2012,Kipping2021,Lingam2024},
a} wide variety of scenarios for the origin of life have been proposed~\citep[e.g.,][]{Baross1985,Brasier2011,Mulkidjanian2012,Fox2013,Deamer2015,Westall2018}.
While we may still be far from conclusively testing these scenarios, new prospects in the search for conditions favorable to life have opened up by thinking of the origin of life as a planetary phenomenon and identifying global-scale environmental properties that might support pathways to life~\citep{Sasselov2020}.
In particular, specific planetary conditions are needed to create stockpiles of initial compounds for prebiotic chemistry; and planetary processes are required to trigger the prebiotic synthesis.
Such planetary conditions can be hypothesized for exoplanets located in the \gls{HZ} of their host star, with persistent liquid water on their surface.
For example, if deep-sea or sedimentary hydrothermalism is required for abiogenesis, then the insulation of an ocean from the planetary crust minerals (e.g., due to high-pressure ices) may reduce or eliminate the chances of life emerging~\citep[e.g.,][]{Baross1985}.
The alternate scenario of a surface locally subject to wet-dry cycles requires a planetary exposure to mid-range \gls{UV} irradiation, as a source of energy and an agent of selection in chemical evolution~\citep[e.g.,][]{Deamer2019}.
This “UV Threshold Hypothesis” states that \gls{UV} light in a specific wavelength range played a constructive role in getting life started on Earth~\citep{Ranjan2016,Ranjan2017c,Rimmer2018,Rapf2016}, and it could provide a probabilistic approach to the interpretation of possible future biosignature detections~\citep[e.g.,][]{Catling2018,Walker2018}.

@@

\section{\rev{Photon Number Fluxes and Energy Fluxes}}\label{appendix:photon_vs_energy_flux}
\rev{The \gls{NUV} fluxes we used in our simulations are given in units of energy flux, i.e., \si{\erg\per\second\per\centi\meter\squared}, due to their availability across different spectral types and evolutionary stages of stars.
Here, we assess the robustness of our conclusions when considering photon number fluxes instead.
}
\rev{We first computed blackbody spectral energy distributions (SEDs) for representative effective temperatures corresponding to K-type, early M-type, and late M-type stars, and across the evolutionary stages considered in the main text.
We then normalized these SEDs to align with the observed UV fluxes from \citet{Richey-Yowell2023} and used them to calculate mean number flux densities (photons \si{\per\centi\meter\squared\per\second\per\nano\meter}) in the \SIrange{200}{280}{\nano\meter} wavelength range.}

>>>>

\section{Introduction}
\label{sec:intro}
\rev{The probability of abiogenesis remains one of the fundamental questions in modern science.
As of now, it has been primarily explored through statistical arguments~\citep[e.g.,][]{Spiegel2012,Kipping2021,Lingam2024}.
At the same time, a} wide variety of scenarios for the origin of life have been proposed~\citep[e.g.,][]{Baross1985,Brasier2011,Mulkidjanian2012,Fox2013,Deamer2015,Westall2018}.
While we may still be far from conclusively testing these scenarios, new prospects in the search for conditions favorable to life have opened up by thinking of the origin of life as a planetary phenomenon and identifying global-scale environmental properties that might support pathways to life~\citep{Sasselov2020}.
In particular, specific planetary conditions are needed to create stockpiles of initial compounds for prebiotic chemistry; and planetary processes are required to trigger the prebiotic synthesis.
Such planetary conditions can be hypothesized for exoplanets located in the \gls{HZ} of their host star, with persistent liquid water on their surface.
For example, if deep-sea or sedimentary hydrothermalism is required for abiogenesis, then the insulation of an ocean from the planetary crust minerals (e.g., due to high-pressure ices) may reduce or eliminate the chances of life emerging~\citep[e.g.,][]{Baross1985}.
The alternate scenario of a surface locally subject to wet-dry cycles requires a planetary exposure to mid-range \gls{UV} irradiation, as a source of energy and an agent of selection in chemical evolution~\citep[e.g.,][]{Deamer2019}.
This “UV Threshold Hypothesis” states that \gls{UV} light in a specific wavelength range played a constructive role in getting life started on Earth~\citep{Ranjan2016,Ranjan2017c,Rimmer2018,Rapf2016}, and it could provide a probabilistic approach to the interpretation of possible future biosignature detections~\citep[e.g.,][]{Catling2018,Walker2018}.

@@

\section{\rev{Photon Number Fluxes and Energy Fluxes}}\label{appendix:photon_vs_energy_flux}
\rev{The \gls{NUV} fluxes we used in our simulations are given in units of energy flux, i.e., \si{\erg\per\second\per\centi\meter\squared}, due to their availability across different spectral types and evolutionary stages of stars.
Here, we assess the robustness of our conclusions when considering photon number fluxes instead.
}
\rev{We first computed blackbody spectral energy distributions (SEDs) for representative effective temperatures corresponding to K-type, early M-type, and late M-type stars, and across the evolutionary stages considered in the main text.
While blackbody SEDs are not necessarily representative of M-dwarf SEDs in the \gls{NUV}~\citep{Seager2013,Rugheimer2015}, the spectrally resolved evolution of M-dwarf SEDs as a function of age is not known; we therefore adopt this simplified prescription for the purpose of this sensitivity test.
We then normalized these SEDs to align with the observed UV fluxes from \citet{Richey-Yowell2023} and used them to calculate mean number flux densities (photons \si{\per\centi\meter\squared\per\second\per\nano\meter}) in the \SIrange{200}{280}{\nano\meter} wavelength range.}
